---
title: "Introduction to the DealGPL570 package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{DealGPL570-introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
#Introduction

GEO provides a wealth of biology related data, and GPL570 (Affymetrix Human Genome U133 Plus 2.0 Array) is one of the the most common biological chip platform.Although the post-processed matrix data are always provided, but the RAW data are most convincing!
Here we developed to deal GPL570 RAW.tar file using the robust multi-array average expression measure, and returns data frame which is expression profile.
Plus: DealGPL570 function can filter cels which are not of GPL570 platform in the RAW.tar file.

#Usage

Load package.

```{r load-package, message=FALSE}
library(DealGPL570)
```

You can put your own `GSE*_RAW.tar` under the working directory, now we download one online and test!
First running this package, you need to keep your device online.

```{r, message=FALSE, eval=FALSE}
GEOquery::getGEOSuppFiles("GSE104683", makeDirectory = FALSE, baseDir = tempdir())
file <- list.files(path = tempdir(), pattern = "GSE104683_RAW.tar", full.names = TRUE)
file
result <- DealGPL570(file = file)
result[1:5, 1:3]
```

When type is "probeID"~

```{r, eval=FALSE}
result <- DealGPL570(file = file, type = "probeID")
result[1:5, 1:2]
```

And when type is "geneSymbol"~

```{r, eval=FALSE}
result <- DealGPL570(file = file, type = "geneSymbol")
result[1:5, 1:2]
```


## Details

For the gene symbols corresponding many probes, we take the median of those probes' expression values as the corresponding gene symbol's expression value.


